---
title: "updated_feedback"
author: "Manasi Patil"
date: "2025-07-22"
output:
  html_document: 
    code_folding: show
    code_download: yes
    highlight: pygments
editor_options: 
  chunk_output_type: inline
---

# Setup

```{r global options setup, include = FALSE}

knitr::opts_chunk$set(
  fig.width = 6,
  # fig.asp = 0.618,
  fig.align = "center",
  out.width = "70%"
)

```

```{r setup}

# load dependencies
library(ggraph)
library(glmnet)
library(here)
library(igraph)
library(textrecipes)
library(tidymodels)
library(tidytext)
library(tidyverse)
library(tm)
library(topicmodels)
library(wordcloud)

```

```{r load data}

updated_feedback <- read_csv(file = here("data", "updated_feedback.csv"))

View(updated_feedback)

```

# Working with tidy text concepts

```{r}

# Unnest tokens and save to a new object #splitted the sentences in word in one column
updated_Feedback_tokens <- updated_feedback %>%
  unnest_tokens(word, Feedback)

# Now view the tokenized data
View(updated_Feedback_tokens)


# View the structure
str(updated_Feedback_tokens)

# Summary stats
summary(updated_Feedback_tokens)

# Frequency like janeaustenr
updated_Feedback_word_counts <- updated_Feedback_tokens %>%
  count(word, sort = TRUE)

# View most common words
head(updated_Feedback_word_counts, 1000)

#Feedback_data_clean

updated_Feedback_data_clean <- updated_Feedback_tokens %>%
  anti_join(get_stopwords(), by = "word")

View(updated_Feedback_data_clean)

#before removing stop words 6,714 entries Feedback_tokens after --> 4,001 Feedback_data_clean


```

# Finding High Frequency of the words

```{r}

updated_Feedback_word_freq <- updated_Feedback_data_clean %>%
  count(word, sort = TRUE)

View(updated_Feedback_word_freq)

# Step 4: View the top words
head(updated_Feedback_word_freq, 20)  # top 20 most frequent words

# Plot top 20 words
updated_Feedback_word_freq %>%
  top_n(30, n) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Frequent Words (After Removing Stop Words)",
       x = "Word", y = "Frequency") +
  theme_minimal()

```

## Bing

```{r}

# Step 1: Join with the Bing sentiment lexicon  
updated_Feedback_sentiment_data <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("bing"), by = "word")


head(updated_Feedback_sentiment_data)


updated_Feedback_sentiment_summary <- updated_Feedback_sentiment_data %>%
  count(sentiment, sort = TRUE)

print(updated_Feedback_sentiment_summary)




ggplot(updated_Feedback_sentiment_summary, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Sentiment Counts from NHS Feedback",
       x = "Sentiment", y = "Count") +
  theme_minimal()
```
## AFINN

```{r}
#---------------Afinn--------------------- Show the score -5 to +5
# Step 1: Load AFINN lexicon and join with cleaned feedback tokens
updated_Feedback_afinn_sentiment <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("afinn"), by = "word")

View(updated_Feedback_afinn_sentiment)
# Step 2: View a few rows to understand the structure
head(updated_Feedback_afinn_sentiment)

# Step 3: Summarize the total sentiment score
updated_Feedback_total_afinn_score <- sum(updated_Feedback_afinn_sentiment$value)
print(paste("Total AFINN sentiment score:", updated_Feedback_total_afinn_score))

# Step 5: Visualize distribution of sentiment scores


ggplot(updated_Feedback_afinn_sentiment, aes(x = updated_Feedback_total_afinn_score)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Sentiment Scores (AFINN)",
       x = "Sentiment Score", y = "Count of Feedbacks") +
  theme_minimal()

```
##NRC
```{r}
#-----------------------NRC-----   count on sentiments for example sentiment ,negative,trust etc
updated_Feedback_nrc_sentiment <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("nrc"), by = "word")

# View first few words and emotions
head(updated_Feedback_nrc_sentiment)

# Count emotions
updated_Feedback_nrc_summary <- updated_Feedback_nrc_sentiment %>%
  count(sentiment, sort = TRUE)

print(updated_Feedback_nrc_summary)



# Filter out only emotion categories (not just positive/negative)
updated_Feedback_nrc_summary %>%
  filter(!sentiment %in% c("positive", "negative")) %>%
  ggplot(aes(x = reorder(sentiment, n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Emotion Distribution in Feedback (NRC)",
       x = "Emotion", y = "Count") +
  theme_minimal()



#Just to check which words falls under negative sentiments

updated_Feedback_nrc_data <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("nrc"), by = "word")

# Filter for negative sentiment
negative_words <- updated_Feedback_nrc_data %>%
  filter(sentiment == "negative")
# View the first few rows
head(negative_words)

#filter for fear sentiment
fear_words <- updated_Feedback_nrc_data %>%
  filter(sentiment == "fear")


# View the first few rows
head(fear_words)

# Count unique words associated with negative sentiment
updated_num_unique_negative_words <- negative_words %>%
  distinct(word) %>%
  count()

print(updated_num_unique_negative_words)
head(updated_num_unique_negative_words)
```
#Comparing three scores together by doing inner join just using common columns from all the lexicons

```{r}


updated_Feedback_afinn_sentiment_C <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(Gender) %>%
  summarise(score = sum(value, na.rm = TRUE)) %>%
  mutate(lexicon = "AFINN")

# Bing sentiment score (positive - negative)
updated_Feedback_sentiment_data_C <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("bing"), by = "word") %>%
  count(Gender, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "Bing") %>%
  select(Gender, score, lexicon)

# NRC sentiment score (positive - negative)
updated_Feedback_nrc_sentiment_C <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  filter(sentiment %in% c("positive", "negative")) %>%
  count(Gender, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "NRC") %>%
  select(Gender, score, lexicon)


# Combine all sentiment scores
updated_all_scores <- bind_rows(updated_Feedback_afinn_sentiment_C, updated_Feedback_sentiment_data_C, updated_Feedback_nrc_sentiment_C)
View(updated_all_scores)


View(updated_Feedback_afinn_sentiment)
View(updated_Feedback_sentiment_data)
View(updated_Feedback_nrc_sentiment)

#Filter to first 20 feedbacks if too many
updated_all_scores_C <- all_scores %>% filter( Gender <= 20)



ggplot(updated_all_scores, aes(x = Gender, y = score, fill = lexicon)) +
  geom_col(position = "dodge") +
  labs(title = "Sentiment Scores by Gender and Lexicon",
       x = "Gender",
       y = "Sentiment Score",
       fill = "Lexicon") +
  theme_minimal()


```
#Trying by adding new ID column to do the analysis
```{r}
View(updated_Feedback_data_clean)

updated_Feedback_data_clean_with_ID <- updated_Feedback_data_clean %>%
  mutate(ID = row_number())
View(updated_Feedback_data_clean_with_ID)

#---              -----------               -------------------
updated_Feedback_afinn_sentiment_C_id <- updated_Feedback_data_clean_with_ID %>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(ID) %>%
  summarise(score = sum(value, na.rm = TRUE)) %>%
  mutate(lexicon = "AFINN")

# Bing sentiment score (positive - negative)
updated_Feedback_sentiment_data_C_id <- updated_Feedback_data_clean_with_ID %>%
  inner_join(get_sentiments("bing"), by = "word") %>%
  count(ID, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "Bing") %>%
  select(ID, score, lexicon)

# NRC sentiment score (positive - negative)
updated_Feedback_nrc_sentiment_C_id <- updated_Feedback_data_clean_with_ID %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  filter(sentiment %in% c("positive", "negative")) %>%
  count(ID, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "NRC") %>%
  select(ID, score, lexicon)


# Combine all sentiment scores
updated_all_scores_ID <- bind_rows(updated_Feedback_afinn_sentiment_C_id, updated_Feedback_sentiment_data_C_id, Feedback_nrc_sentiment_C_id)
View(updated_all_scores_ID)


View(updated_Feedback_afinn_sentiment_C_id)
View(updated_Feedback_sentiment_data_C_id)
View(updated_Feedback_nrc_sentiment_C_id)

#Filter to first 20 feedbacks if too many
updated_all_scores_C_id_1 <- updated_all_scores_ID %>% filter( ID <= 20)



ggplot(updated_all_scores_C_id_1, aes(x = ID, y = score, fill = lexicon)) +
  geom_col(position = "dodge") +
  labs(title = "Sentiment Scores by Gender and Lexicon",
       x = "Gender",
       y = "Sentiment Score",
       fill = "Lexicon") +
  theme_minimal()


```
# WordCloud

```{r}


updated_Feedback_tokens %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))



updated_Feedback_tokens %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)


```

#Term Frequency - How often the word is used in the document
```{r}



updated_Feedback_term_freq <- updated_Feedback_tokens %>%
  count(word, sort = TRUE)

head(updated_Feedback_term_freq, 60)  # Top 60 most frequent words


View(updated_Feedback_term_freq)
View(updated_Feedback_tokens)

#--------Trying by adding new ID column to do the analysis---
updated_Feedback_tokens_ID <- updated_Feedback_tokens %>%
  mutate(ID = row_number())
View(updated_Feedback_tokens_ID)

updated_Feedback_term_freq_by_id <- updated_Feedback_tokens_ID %>%
  count(ID, word, sort = TRUE)

head(updated_Feedback_term_freq_by_id, 20)



# Top 20 overall terms
updated_Feedback_top_terms <- updated_Feedback_term_freq_by_id %>%
  top_n(20, n) %>%
  mutate(word = reorder(word, n))

ggplot(Feedback_top_terms, aes(x = word, y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Frequent words",
       x = "Word", y = "Frequency") +
  theme_minimal(10)

View(updated_Feedback_top_terms)

#---Not grouped by ID
# Step 1: Get total word frequency (ignoring ID)
updated_Feedback_top_terms <- updated_Feedback_term_freq_by_id %>%
  group_by(word) %>%
  summarise(n = sum(n), .groups = "drop") %>%
  slice_max(n, n = 50) %>%
  mutate(word = reorder(word, n))

# Step 2: Plot
ggplot(updated_Feedback_top_terms, aes(x = word, y = n)) +
  geom_col(fill = "steelblue") +
  
  coord_flip() +
  labs(title = "Top 20 Frequent Words",
       x = "Word", y = "Frequency") +
  theme_minimal()

```


#TF-IDF
```{r}
#-----------TF_IDF-----------------#
# Step 1: Compute TF-IDF 
# Term frequency how often a word appears in a single document 

#IDF (Inverse Document Frequency) = how rare that word is across all documents 

updated_Feed_back_tfidf <- updated_Feedback_tokens_ID %>%
  count(ID, word, sort = TRUE) %>%  # X is the document ID
  bind_tf_idf(word, ID, n) %>%
  arrange(desc(tf_idf))

# Step 2: View top TF-IDF words
head(updated_Feed_back_tfidf, 50)

#-------------Top words per feedback--------------

updated_Feedback_top_tfidf_words <- updated_Feed_back_tfidf %>%
  group_by(ID) %>%
  slice_max(tf_idf, n = 5) %>%
  ungroup()

head(updated_Feedback_top_tfidf_words)

# For a specific feedback ID (example: ID 15)
updated_Feed_back_tfidf %>%
  filter(ID == 350) %>%
  slice_max(tf_idf, n = 10) %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col(fill = "darkgreen") +
  coord_flip() +
  labs(title = "Top TF-IDF words for Feedback ID 15",
       x = "Word", y = "TF-IDF Score") +
  theme_minimal()

#topic modelling used to combine similar topic related words together





# 1. Create a Document-Term Matrix
updated_dtm <- Feedback_tokens_ID %>%
  count(ID, word) %>%
  cast_dtm(document = ID, term = word, value = n)

View(updated_dtm)

# 2. Fit the LDA Model (3 topics here, change k as needed)
updated_lda_model <- LDA(updated_dtm, k = 3, control = list(seed = 1234))
View(updated_lda_model)
# 3. Tidy the model output
updated_topics <- tidy(updated_lda_model, matrix = "beta")  # beta = prob of word in topic
View(updated_topics)
# 4. Get top 100 terms per topic
updated_top_terms <- updated_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

View(updated_top_terms)

# 5. Visualize top words in each topic

updated_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Words in Each Topic", x = "Word", y = "Probability")

```


#---------Bigrams and Trigrams-----------------
```{r}
#instead of looking at single word we look at 2 words or triplets to better understanding
View(updated_feedback)
# 1. Extract Bigrams
updated_Feedback_bigrams <- updated_feedback %>%
  unnest_tokens(bigram, Feedback, token = "ngrams", n = 2)
View(updated_Feedback_bigrams)

# 2. Split bigrams into word1 and word2
updated_Feedback_bigrams_separated <- updated_Feedback_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

View("updated_Feedback_bigrams_separated")

# 3. Remove stop words(you can see reduced rows)
updated_Feedback_bigrams_filtered <- Feedback_bigrams_separated %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word)

View(updated_Feedback_bigrams_filtered)

# 4. Count cleaned bigrams
updated_Feedback_bigram_counts <- updated_Feedback_bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ") %>%
  count(bigram, sort = TRUE)

# 5. View top bigrams
head(updated_Feedback_bigram_counts, 20)


#------------------------Visualization for Bigrams--------------------------------



# Create a graph object
updated_Feedback_bigram_graph <- updated_Feedback_bigram_counts %>%
  filter(n > 5) %>%  # Keep only frequently occurring bigrams
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  graph_from_data_frame()

# Plot the network
ggraph(updated_Feedback_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 4) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void() +
  labs(title = "Bigram Network from NHS Feedback")


```


#-------------Compare word usage by group ie :gender and clinical

```{r}
View(updated_feedback)
updated_Feedback_words <- updated_feedback %>%
  unnest_tokens(word, Feedback) %>%
  anti_join(stop_words)

# Count word usage by Gender
updated_word_gender <- updated_Feedback_words %>%
  count(word, Gender) %>%
  group_by(word) %>%
  filter(sum(n) > 10) %>%  # Words used at least 10 times
  spread(Gender, n, fill = 0) %>%
  mutate(log_ratio = log2((M + 1) / (F + 1)))
View(updated_word_gender)

# Visualize top gendered words
updated_word_gender %>%
  arrange(desc(abs(log_ratio))) %>%
  top_n(10, abs(log_ratio)) %>%
  ggplot(aes(x = reorder(word, log_ratio), y = log_ratio, fill = log_ratio > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Words Associated with Each Gender",
       x = "Word", y = "Log Ratio (M / F)") +
  scale_fill_manual(values = c("pink", "skyblue"))

#-----------Trying for Clinical------------
# Count word usage by Gender
updated_word_clinical <- updated_Feedback_words %>%
  count(word, Clinical.Y.N) %>%
  group_by(word) %>%
  filter(sum(n) > 10) %>%  # Words used at least 10 times
  spread(Clinical.Y.N, n, fill = 0) %>%
  mutate(log_ratio = log2((Y + 1) / (N + 1)))
View(updated_word_clinical)

# Visualize top gendered words
updated_word_clinical %>%
  arrange(desc(abs(log_ratio))) %>%
  top_n(10, abs(log_ratio)) %>%
  ggplot(aes(x = reorder(word, log_ratio), y = log_ratio, fill = log_ratio > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Words Associated with Each Gender",
       x = "Word", y = "Log Ratio (Y/ N)") +
  scale_fill_manual(values = c("pink", "skyblue"))


```

#---------Topic Modeling with LDA-----------------#
```{r}




# Create Document-Term Matrix
updated_dtm_1 <- updated_Feedback_tokens_ID %>%
  count(ID, word) %>%
  cast_dtm(document = ID, term = word, value = n)
View(updated_dtm_1)


# Fit the LDA model with k = 3 topics
updated_lda_model_1 <- LDA(updated_dtm, k = 3, control = list(seed = 1234))
View(updated_lda_model_1)

# Tidy the LDA output


updated_topics_1 <- tidy(lda_model, matrix = "beta")

# Get top 10 terms per topic
updated_top_terms_1 <- updated_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

View(updated_top_terms_1)




top_terms_1 %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Words per Topic (LDA)",
       x = "Word", y = "Probability")


# Document-topic probabilities
updated_document_topics_1 <- tidy(updated_lda_model, matrix = "gamma")

# For each feedback, find the most probable topic
updated_top_feedback_topics_1 <- document_topics_1 %>%
  group_by(document) %>%
  slice_max(gamma, n = 1)

View(updated_top_feedback_topics_1)


```
#----------Formalise testing for afinn--------
```{r}
# Merge sentiment scores (AFINN) with original Feedback data to get Clinical label
updated_afinn_scores_with_clinical <- updated_Feedback_afinn_sentiment_C_id %>%
  left_join(Feedback %>% mutate(ID = row_number()) %>% select(ID, Clinical.Y.N), by = "ID")

# View to confirm
View(updated_afinn_scores_with_clinical)


str(updated_afinn_scores_with_clinical)
table(updated_afinn_scores_with_clinical$Clinical.Y.N)


#Checking normality for each clinical group
shapiro.test(updated_afinn_scores_with_clinical$score[updated_afinn_scores_with_clinical$Clinical.Y.N == "Y"])
shapiro.test(updated_afinn_scores_with_clinical$score[updated_afinn_scores_with_clinical$Clinical.Y.N == "N"])




ggplot(updated_afinn_scores_with_clinical, aes(x = Clinical.Y.N, y = score, fill = Clinical.Y.N)) +
  geom_boxplot() +
  labs(title = "Sentiment Score by Clinical Review Group (AFINN)",
       x = "Clinical Review (Y/N)",
       y = "AFINN Sentiment Score") +
  theme_minimal()


#QQ-plot
ggplot(updated_afinn_scores_with_clinical, aes(sample = score)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~Clinical.Y.N) +
  labs(title = "Q-Q Plot of AFINN Sentiment Score by Clinical Group",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") +
  theme_minimal()

#output : data:  afinn_scores_with_clinical$score[afinn_scores_with_clinical$Clinical.Y.N == "Y"]
#W = 0.82045, p-value = 0.0006486 -------------------> For Y

#data:  afinn_scores_with_clinical$score[afinn_scores_with_clinical$Clinical.Y.N == "N"]
#W = 0.81543, p-value = 0.01502 -----------------------> For N


#Since both groups fail the normality test (p < 0.05), you must use a non-parametric test:
wilcox.test(score ~ Clinical.Y.N, data = updated_afinn_scores_with_clinical)


wilcox.test(score ~ Clinical.Y.N, data = updated_afinn_scores_with_clinical, exact = FALSE)
#There is no significant difference in AFINN sentiment scores between Clinical = Y and Clinical = N groups as p-value < 0.05
#W = 119.5, p-value = 0.661


```

---
title: "updated_feedback"
author: "Manasi Patil"
date: "2025-07-02"
output: html_document
---

#Library
```{r}
install.packages("janitor")
install.packages("here")

```

#Loading the file
```{r}
updated_feedback <- read.csv("C:/Users/Manasi/Documents/Tidy Text/updated_feedback.csv")

View(updated_feedback)

```

#Working with tidy text concepts
```{r}



# Unnest tokens and save to a new object #splitted the sentences in word in one column
updated_Feedback_tokens <- updated_feedback %>%
  unnest_tokens(word, Feedback)

# Now view the tokenized data
View(updated_Feedback_tokens)


# View the structure
str(updated_Feedback_tokens)

# Summary stats
summary(updated_Feedback_tokens)

# Frequency like janeaustenr
updated_Feedback_word_counts <- updated_Feedback_tokens %>%
  count(word, sort = TRUE)

# View most common words
head(updated_Feedback_word_counts, 1000)

#Feedback_data_clean

updated_Feedback_data_clean <- updated_Feedback_tokens %>%
  anti_join(get_stopwords(), by = "word")

View(updated_Feedback_data_clean)

#before removing stop words 6,714 entries Feedback_tokens after --> 4,001 Feedback_data_clean


```

#Finding High Frequency of the words
```{r}
updated_Feedback_word_freq <- updated_Feedback_data_clean %>%
  count(word, sort = TRUE)

View(updated_Feedback_word_freq)

# Step 4: View the top words
head(updated_Feedback_word_freq, 20)  # top 20 most frequent words




# Plot top 20 words
updated_Feedback_word_freq %>%
  top_n(30, n) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Frequent Words (After Removing Stop Words)",
       x = "Word", y = "Frequency") +
  theme_minimal()

```
## Bing
```{r}



# Step 1: Join with the Bing sentiment lexicon  
updated_Feedback_sentiment_data <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("bing"), by = "word")


head(updated_Feedback_sentiment_data)


updated_Feedback_sentiment_summary <- updated_Feedback_sentiment_data %>%
  count(sentiment, sort = TRUE)

print(updated_Feedback_sentiment_summary)




ggplot(updated_Feedback_sentiment_summary, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Sentiment Counts from NHS Feedback",
       x = "Sentiment", y = "Count") +
  theme_minimal()
```
## AFINN

```{r}
#---------------Afinn--------------------- Show the score -5 to +5
# Step 1: Load AFINN lexicon and join with cleaned feedback tokens
updated_Feedback_afinn_sentiment <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("afinn"), by = "word")

View(updated_Feedback_afinn_sentiment)
# Step 2: View a few rows to understand the structure
head(updated_Feedback_afinn_sentiment)

# Step 3: Summarize the total sentiment score
updated_Feedback_total_afinn_score <- sum(updated_Feedback_afinn_sentiment$value)
print(paste("Total AFINN sentiment score:", updated_Feedback_total_afinn_score))

# Step 5: Visualize distribution of sentiment scores


ggplot(updated_Feedback_afinn_sentiment, aes(x = updated_Feedback_total_afinn_score)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Sentiment Scores (AFINN)",
       x = "Sentiment Score", y = "Count of Feedbacks") +
  theme_minimal()

```
##NRC
```{r}
#-----------------------NRC-----   count on sentiments for example sentiment ,negative,trust etc
updated_Feedback_nrc_sentiment <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("nrc"), by = "word")

# View first few words and emotions
head(updated_Feedback_nrc_sentiment)

# Count emotions
updated_Feedback_nrc_summary <- updated_Feedback_nrc_sentiment %>%
  count(sentiment, sort = TRUE)

print(updated_Feedback_nrc_summary)



# Filter out only emotion categories (not just positive/negative)
updated_Feedback_nrc_summary %>%
  filter(!sentiment %in% c("positive", "negative")) %>%
  ggplot(aes(x = reorder(sentiment, n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Emotion Distribution in Feedback (NRC)",
       x = "Emotion", y = "Count") +
  theme_minimal()



#Just to check which words falls under negative sentiments

updated_Feedback_nrc_data <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("nrc"), by = "word")

# Filter for negative sentiment
negative_words <- updated_Feedback_nrc_data %>%
  filter(sentiment == "negative")
# View the first few rows
head(negative_words)

#filter for fear sentiment
fear_words <- updated_Feedback_nrc_data %>%
  filter(sentiment == "fear")


# View the first few rows
head(fear_words)

# Count unique words associated with negative sentiment
updated_num_unique_negative_words <- negative_words %>%
  distinct(word) %>%
  count()

print(updated_num_unique_negative_words)
head(updated_num_unique_negative_words)
```
#Comparing three scores together by doing inner join just using common columns from all the lexicons

```{r}


updated_Feedback_afinn_sentiment_C <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(Gender) %>%
  summarise(score = sum(value, na.rm = TRUE)) %>%
  mutate(lexicon = "AFINN")

# Bing sentiment score (positive - negative)
updated_Feedback_sentiment_data_C <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("bing"), by = "word") %>%
  count(Gender, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "Bing") %>%
  select(Gender, score, lexicon)

# NRC sentiment score (positive - negative)
updated_Feedback_nrc_sentiment_C <- updated_Feedback_data_clean %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  filter(sentiment %in% c("positive", "negative")) %>%
  count(Gender, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "NRC") %>%
  select(Gender, score, lexicon)


# Combine all sentiment scores
updated_all_scores <- bind_rows(updated_Feedback_afinn_sentiment_C, updated_Feedback_sentiment_data_C, updated_Feedback_nrc_sentiment_C)
View(updated_all_scores)


View(updated_Feedback_afinn_sentiment)
View(updated_Feedback_sentiment_data)
View(updated_Feedback_nrc_sentiment)

#Filter to first 20 feedbacks if too many
updated_all_scores_C <- all_scores %>% filter( Gender <= 20)



ggplot(updated_all_scores, aes(x = Gender, y = score, fill = lexicon)) +
  geom_col(position = "dodge") +
  labs(title = "Sentiment Scores by Gender and Lexicon",
       x = "Gender",
       y = "Sentiment Score",
       fill = "Lexicon") +
  theme_minimal()


```
#Trying by adding new ID column to do the analysis
```{r}
View(updated_Feedback_data_clean)

updated_Feedback_data_clean_with_ID <- updated_Feedback_data_clean %>%
  mutate(ID = row_number())
View(updated_Feedback_data_clean_with_ID)

#---              -----------               -------------------
updated_Feedback_afinn_sentiment_C_id <- updated_Feedback_data_clean_with_ID %>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(ID) %>%
  summarise(score = sum(value, na.rm = TRUE)) %>%
  mutate(lexicon = "AFINN")

# Bing sentiment score (positive - negative)
updated_Feedback_sentiment_data_C_id <- updated_Feedback_data_clean_with_ID %>%
  inner_join(get_sentiments("bing"), by = "word") %>%
  count(ID, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "Bing") %>%
  select(ID, score, lexicon)

# NRC sentiment score (positive - negative)
updated_Feedback_nrc_sentiment_C_id <- updated_Feedback_data_clean_with_ID %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  filter(sentiment %in% c("positive", "negative")) %>%
  count(ID, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(score = positive - negative,
         lexicon = "NRC") %>%
  select(ID, score, lexicon)


# Combine all sentiment scores
updated_all_scores_ID <- bind_rows(updated_Feedback_afinn_sentiment_C_id, updated_Feedback_sentiment_data_C_id, Feedback_nrc_sentiment_C_id)
View(updated_all_scores_ID)


View(updated_Feedback_afinn_sentiment_C_id)
View(updated_Feedback_sentiment_data_C_id)
View(updated_Feedback_nrc_sentiment_C_id)

#Filter to first 20 feedbacks if too many
updated_all_scores_C_id_1 <- updated_all_scores_ID %>% filter( ID <= 20)



ggplot(updated_all_scores_C_id_1, aes(x = ID, y = score, fill = lexicon)) +
  geom_col(position = "dodge") +
  labs(title = "Sentiment Scores by Gender and Lexicon",
       x = "Gender",
       y = "Sentiment Score",
       fill = "Lexicon") +
  theme_minimal()


```
# WordCloud

```{r}


updated_Feedback_tokens %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))



updated_Feedback_tokens %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)


```

#Term Frequency - How often the word is used in the document
```{r}



updated_Feedback_term_freq <- updated_Feedback_tokens %>%
  count(word, sort = TRUE)

head(updated_Feedback_term_freq, 60)  # Top 60 most frequent words


View(updated_Feedback_term_freq)
View(updated_Feedback_tokens)

#--------Trying by adding new ID column to do the analysis---
updated_Feedback_tokens_ID <- updated_Feedback_tokens %>%
  mutate(ID = row_number())
View(updated_Feedback_tokens_ID)

updated_Feedback_term_freq_by_id <- updated_Feedback_tokens_ID %>%
  count(ID, word, sort = TRUE)

head(updated_Feedback_term_freq_by_id, 20)



# Top 20 overall terms
updated_Feedback_top_terms <- updated_Feedback_term_freq_by_id %>%
  top_n(20, n) %>%
  mutate(word = reorder(word, n))

ggplot(Feedback_top_terms, aes(x = word, y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Frequent words",
       x = "Word", y = "Frequency") +
  theme_minimal(10)

View(updated_Feedback_top_terms)

#---Not grouped by ID
# Step 1: Get total word frequency (ignoring ID)
updated_Feedback_top_terms <- updated_Feedback_term_freq_by_id %>%
  group_by(word) %>%
  summarise(n = sum(n), .groups = "drop") %>%
  slice_max(n, n = 50) %>%
  mutate(word = reorder(word, n))

# Step 2: Plot
ggplot(updated_Feedback_top_terms, aes(x = word, y = n)) +
  geom_col(fill = "steelblue") +
  
  coord_flip() +
  labs(title = "Top 20 Frequent Words",
       x = "Word", y = "Frequency") +
  theme_minimal()

```


#TF-IDF
```{r}
#-----------TF_IDF-----------------#
# Step 1: Compute TF-IDF 
# Term frequency how often a word appears in a single document 

#IDF (Inverse Document Frequency) = how rare that word is across all documents 

updated_Feed_back_tfidf <- updated_Feedback_tokens_ID %>%
  count(ID, word, sort = TRUE) %>%  # X is the document ID
  bind_tf_idf(word, ID, n) %>%
  arrange(desc(tf_idf))

# Step 2: View top TF-IDF words
head(updated_Feed_back_tfidf, 50)

#-------------Top words per feedback--------------

updated_Feedback_top_tfidf_words <- updated_Feed_back_tfidf %>%
  group_by(ID) %>%
  slice_max(tf_idf, n = 5) %>%
  ungroup()

head(updated_Feedback_top_tfidf_words)

# For a specific feedback ID (example: ID 15)
updated_Feed_back_tfidf %>%
  filter(ID == 350) %>%
  slice_max(tf_idf, n = 10) %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col(fill = "darkgreen") +
  coord_flip() +
  labs(title = "Top TF-IDF words for Feedback ID 15",
       x = "Word", y = "TF-IDF Score") +
  theme_minimal()

#topic modelling used to combine similar topic related words together





# 1. Create a Document-Term Matrix
updated_dtm <- Feedback_tokens_ID %>%
  count(ID, word) %>%
  cast_dtm(document = ID, term = word, value = n)

View(updated_dtm)

# 2. Fit the LDA Model (3 topics here, change k as needed)
updated_lda_model <- LDA(updated_dtm, k = 3, control = list(seed = 1234))
View(updated_lda_model)
# 3. Tidy the model output
updated_topics <- tidy(updated_lda_model, matrix = "beta")  # beta = prob of word in topic
View(updated_topics)
# 4. Get top 100 terms per topic
updated_top_terms <- updated_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

View(updated_top_terms)

# 5. Visualize top words in each topic

updated_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Words in Each Topic", x = "Word", y = "Probability")

```


#---------Bigrams and Trigrams-----------------
```{r}
#instead of looking at single word we look at 2 words or triplets to better understanding
View(updated_feedback)
# 1. Extract Bigrams
updated_Feedback_bigrams <- updated_feedback %>%
  unnest_tokens(bigram, Feedback, token = "ngrams", n = 2)
View(updated_Feedback_bigrams)

# 2. Split bigrams into word1 and word2
updated_Feedback_bigrams_separated <- updated_Feedback_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

View("updated_Feedback_bigrams_separated")

# 3. Remove stop words(you can see reduced rows)
updated_Feedback_bigrams_filtered <- Feedback_bigrams_separated %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word)

View(updated_Feedback_bigrams_filtered)

# 4. Count cleaned bigrams
updated_Feedback_bigram_counts <- updated_Feedback_bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ") %>%
  count(bigram, sort = TRUE)

# 5. View top bigrams
head(updated_Feedback_bigram_counts, 20)


#------------------------Visualization for Bigrams--------------------------------



# Create a graph object
updated_Feedback_bigram_graph <- updated_Feedback_bigram_counts %>%
  filter(n > 5) %>%  # Keep only frequently occurring bigrams
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  graph_from_data_frame()

# Plot the network
ggraph(updated_Feedback_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 4) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void() +
  labs(title = "Bigram Network from NHS Feedback")


```


#-------------Compare word usage by group ie :gender and clinical

```{r}
View(updated_feedback)
updated_Feedback_words <- updated_feedback %>%
  unnest_tokens(word, Feedback) %>%
  anti_join(stop_words)

# Count word usage by Gender
updated_word_gender <- updated_Feedback_words %>%
  count(word, Gender) %>%
  group_by(word) %>%
  filter(sum(n) > 10) %>%  # Words used at least 10 times
  spread(Gender, n, fill = 0) %>%
  mutate(log_ratio = log2((M + 1) / (F + 1)))
View(updated_word_gender)

# Visualize top gendered words
updated_word_gender %>%
  arrange(desc(abs(log_ratio))) %>%
  top_n(10, abs(log_ratio)) %>%
  ggplot(aes(x = reorder(word, log_ratio), y = log_ratio, fill = log_ratio > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Words Associated with Each Gender",
       x = "Word", y = "Log Ratio (M / F)") +
  scale_fill_manual(values = c("pink", "skyblue"))

#-----------Trying for Clinical------------
# Count word usage by Gender
updated_word_clinical <- updated_Feedback_words %>%
  count(word, Clinical.Y.N) %>%
  group_by(word) %>%
  filter(sum(n) > 10) %>%  # Words used at least 10 times
  spread(Clinical.Y.N, n, fill = 0) %>%
  mutate(log_ratio = log2((Y + 1) / (N + 1)))
View(updated_word_clinical)

# Visualize top gendered words
updated_word_clinical %>%
  arrange(desc(abs(log_ratio))) %>%
  top_n(10, abs(log_ratio)) %>%
  ggplot(aes(x = reorder(word, log_ratio), y = log_ratio, fill = log_ratio > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Words Associated with Each Gender",
       x = "Word", y = "Log Ratio (Y/ N)") +
  scale_fill_manual(values = c("pink", "skyblue"))


```

#---------Topic Modeling with LDA-----------------#
```{r}




# Create Document-Term Matrix
updated_dtm_1 <- updated_Feedback_tokens_ID %>%
  count(ID, word) %>%
  cast_dtm(document = ID, term = word, value = n)
View(updated_dtm_1)


# Fit the LDA model with k = 3 topics
updated_lda_model_1 <- LDA(updated_dtm, k = 3, control = list(seed = 1234))
View(updated_lda_model_1)

# Tidy the LDA output


updated_topics_1 <- tidy(lda_model, matrix = "beta")

# Get top 10 terms per topic
updated_top_terms_1 <- updated_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

View(updated_top_terms_1)




top_terms_1 %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Words per Topic (LDA)",
       x = "Word", y = "Probability")


# Document-topic probabilities
updated_document_topics_1 <- tidy(updated_lda_model, matrix = "gamma")

# For each feedback, find the most probable topic
updated_top_feedback_topics_1 <- document_topics_1 %>%
  group_by(document) %>%
  slice_max(gamma, n = 1)

View(updated_top_feedback_topics_1)


```
#----------Formalise testing for afinn--------
```{r}
# Merge sentiment scores (AFINN) with original Feedback data to get Clinical label
afinn_scores_with_clinical <- Feedback_afinn_sentiment_C_id %>%
  left_join(Feedback %>% mutate(ID = row_number()) %>% select(ID, Clinical.Y.N), by = "ID")

# View to confirm
View(afinn_scores_with_clinical)


str(afinn_scores_with_clinical)
table(afinn_scores_with_clinical$Clinical.Y.N)


#Checking normality for each clinical group
shapiro.test(afinn_scores_with_clinical$score[afinn_scores_with_clinical$Clinical.Y.N == "Y"])
shapiro.test(afinn_scores_with_clinical$score[afinn_scores_with_clinical$Clinical.Y.N == "N"])




ggplot(afinn_scores_with_clinical, aes(x = Clinical.Y.N, y = score, fill = Clinical.Y.N)) +
  geom_boxplot() +
  labs(title = "Sentiment Score by Clinical Review Group (AFINN)",
       x = "Clinical Review (Y/N)",
       y = "AFINN Sentiment Score") +
  theme_minimal()


#QQ-plot
ggplot(afinn_scores_with_clinical, aes(sample = score)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~Clinical.Y.N) +
  labs(title = "Q-Q Plot of AFINN Sentiment Score by Clinical Group",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") +
  theme_minimal()

#output : data:  afinn_scores_with_clinical$score[afinn_scores_with_clinical$Clinical.Y.N == "Y"]
#W = 0.82045, p-value = 0.0006486 -------------------> For Y

#data:  afinn_scores_with_clinical$score[afinn_scores_with_clinical$Clinical.Y.N == "N"]
#W = 0.81543, p-value = 0.01502 -----------------------> For N


#Since both groups fail the normality test (p < 0.05), you must use a non-parametric test:
wilcox.test(score ~ Clinical.Y.N, data = afinn_scores_with_clinical)


wilcox.test(score ~ Clinical.Y.N, data = afinn_scores_with_clinical, exact = FALSE)
#There is no significant difference in AFINN sentiment scores between Clinical = Y and Clinical = N groups as p-value < 0.05
#W = 119.5, p-value = 0.661



```
#BING
```{r}
# Merge sentiment scores (BING) with original Feedback data to get Clinical label
updated_bing_scores_with_clinical <- updated_Feedback_sentiment_data_C_id %>%
  left_join(Feedback %>% mutate(ID = row_number()) %>% select(ID, Clinical.Y.N), by = "ID")

# View to confirm
View(updated_bing_scores_with_clinical)


str(updated_bing_scores_with_clinical)
table(updated_bing_scores_with_clinical)


#Checking normality for each clinical group
shapiro.test(updated_bing_scores_with_clinical$score[updated_bing_scores_with_clinical$Clinical.Y.N == "Y"])
#W = 0.57309, p-value = 9.018e-09

shapiro.test(updated_bing_scores_with_clinical$score[updated_bing_scores_with_clinical$Clinical.Y.N == "N"])
#W = 0.48429, p-value = 1.575e-06



ggplot(updated_bing_scores_with_clinical, aes(x = Clinical.Y.N, y = score, fill = Clinical.Y.N)) +
  geom_boxplot() +
  labs(title = "Sentiment Score by Clinical Review Group (Bing)",
       x = "Clinical Review (Y/N)",
       y = "Bing Sentiment Score") +
  theme_minimal()


#QQ-plot
ggplot(updated_bing_scores_with_clinical, aes(sample = score)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~Clinical.Y.N) +
  labs(title = "Q-Q Plot of Bing Sentiment Score by Clinical Group",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") +
  theme_minimal()

#Since both p-values are < 0.05, the sentiment scores for both groups do not follow a normal distribution.
#using non-parametric test
wilcox.test(score ~ Clinical.Y.N, data = updated_bing_scores_with_clinical)

wilcox.test(score ~ Clinical.Y.N, data = updated_bing_scores_with_clinical, exact = FALSE)
#data:  score by Clinical.Y.N
#W = 243, p-value = 0.4354
#does not differ significantly as p value is not <0.05



```
#NRC
```{r}
#-----------------------------------NRC--------------------------------------
# Merge sentiment scores (AFINN) with original Feedback data to get Clinical label
updated_nrc_scores_with_clinical <- updated_Feedback_nrc_sentiment_C_id%>%
  left_join(Feedback %>% mutate(ID = row_number()) %>% select(ID, Clinical.Y.N), by = "ID")

# View to confirm
View(updated_nrc_scores_with_clinical)


str(updated_nrc_scores_with_clinical)
table(updated_nrc_scores_with_clinical)


#Checking normality for each clinical group
shapiro.test(updated_nrc_scores_with_clinical$score[updated_nrc_scores_with_clinical$Clinical.Y.N == "Y"])
#W = 0.62249, p-value = 1.608e-06

shapiro.test(updated_nrc_scores_with_clinical$score[updated_nrc_scores_with_clinical$Clinical.Y.N == "N"])
#W = 0.64917, p-value = 0.0001052



ggplot(updated_nrc_scores_with_clinical, aes(x = Clinical.Y.N, y = score, fill = Clinical.Y.N)) +
  geom_boxplot() +
  labs(title = "Sentiment Score by Clinical Review Group (NRC)",
       x = "Clinical Review (Y/N)",
       y = "Bing Sentiment Score") +
  theme_minimal()


#QQ-plot
ggplot(updated_nrc_scores_with_clinical, aes(sample = score)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~Clinical.Y.N) +
  labs(title = "Q-Q Plot of NRC Sentiment Score by Clinical Group",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") +
  theme_minimal()

#Since both groups fail the normality test (p < 0.05), you must use a non-parametric test:
wilcox.test(score ~ Clinical.Y.N, data = updated_nrc_scores_with_clinical, exact = FALSE)
#data:  score by Clinical.Y.N
#W = 134.5, p-value = 0.7461

```
#Modelling
```{r}
#----------------------------Modelling-------------------------------




#As factor
feedback_modelling <- Feedback %>%
  mutate(Clinical.Y.N = as.factor(Clinical.Y.N))

View(feedback_modelling)


#train/test split
set.seed(123)
feedback_split <- initial_split(feedback_modelling, strata = Clinical.Y.N)
train_data <- training(feedback_split)
test_data <- testing(feedback_split)

View(train_data)
View(test_data)

#This converts text into tokens, removes stopwords, applies TF-IDF:

feedback_recipe <- recipe(Clinical.Y.N ~ Feedback, data = train_data) %>%
  step_tokenize(Feedback) %>%
  step_stopwords(Feedback) %>%
  step_tokenfilter(Feedback, max_tokens = 400) %>%
  step_tfidf(Feedback)
View(feedback_recipe)


#using logistic regression
log_model <- logistic_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet") %>%
  set_mode("classification")
View(log_model)
#workflow
feedback_workflow <- workflow() %>%
  add_model(log_model) %>%
  add_recipe(feedback_recipe)
View(feedback_workflow)


#cross validation + tuning
set.seed(234)
feedback_folds <- vfold_cv(train_data, v = 5, strata = Clinical.Y.N)

View(feedback_folds)

install.packages("glmnet")



feedback_tune <- tune_grid(
  feedback_workflow,
  resamples = feedback_folds,
  grid = 10,
  metrics = metric_set(accuracy, roc_auc)
)

View(feedback_tune)


#Select the best model

best_model <- select_best(feedback_tune, metric = "roc_auc")

final_workflow <- finalize_workflow(feedback_workflow, best_model)


#final model evaluation

final_fit <- last_fit(final_workflow, feedback_split)

collect_metrics(final_fit)
collect_predictions(final_fit) %>%
  conf_mat(truth = Clinical.Y.N, estimate = .pred_class)

#--------------Testing the model on sample feedbacks----------------------------------
fitted_model <- fit(final_workflow, data = train_data)

Sample_feedback <- tibble(                         #this is the feedback random generated by chatgpt
                                                   #Gives correct prediction 1 N ,2 Y ,3 Y,4 Y 
  Feedback = c(
    "The app is extremely helpful and easy to use.",
    "Terrible experience, couldn't get any help.",
    "Not bad, but needs improvement in loading speed.",
    "I have a chest pain." 
    )
)
View(Sample_feedback)
predict(fitted_model, new_data = Sample_feedback)
predict(fitted_model, new_data = Sample1_feedback)

Sample1_feedback <- tibble( #I tested on the sythentic dataset feedbacks it gives write answers ie:Y,N,N,Y
  Feedback = c(
    "I’ve been experiencing joint stiffness that feels sharp.",
    "I app logs me out randomly, despite updating it multiple times",
    "I app logs me out randomly, no matter how many times I try",
    "I have a chest pain." 
  )
)

```


